Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-24 article/article.tex
Commit 2024-05-24 12:16

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of CE occurrences. We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance of the atmosphere. The net solar radiation of the
region is not increased, but rather redistributed through the CE events.
This also is depicted by the ``instantaneous'' values of irradiance
(average over one minute), that can exceed the equivalent clear sky
irradiance to a considerable level.

@@

By creating a clear sky approximation of the GHI, which can represent
the long- and short-term variation of the expected clear sky GHI, we
were able to identify cases of CE events. By analysing the CE cases we
found

The climatology of CE occurrences over the whole period and

the magnitude of the CE events. We estabished the occurances of extreme
CE events \ldots{} The characteristic of the duration of ``continuous''
CE events. with their magnitude occurnacies and climatology

@@

The interaction of GHI with the clouds through this period shows a
systematic change.

@@

Climatology results

>>>>

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,\text{kj}/\text{year}\)
(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
of CE occurrences. We have to note that the energy related to the CE
events can not be directly linked with the total energy balance of the
atmosphere. The net solar radiation of the region is not increased, but
rather redistributed through the CE events. This also is depicted by the
``instantaneous'' values of irradiance (average over one minute), that
can exceed the equivalent clear sky irradiance to a considerable level.

@@

By creating a clear sky approximation of the GHI, which can represent
the long- and short-term variation of the expected clear sky GHI, we
were able to identify cases of CE events. By analyzing the CE cases we
found an increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\), with
the mean annual total energy of the CE events increasing with a rate of
\(116.9\pm 67.8\,\text{kj}/\text{year}\). The most active season of CE
events over Thessaloniki is concentrated on early summer, on May and
June.

The magnitude of the ECE events doesn't exceeds the values reported from
sites with more favorable conditions for the phenomenon. Although, the
climatological characteristic of the ECE events, showed that the most
active months are spread on half of the year (March -- June and
September and October).

We find that CE conditions can have a duration of more than an hour in
rare cases, with the bulk of the cases having a duration under 5
minutes.

@@

An interpretation of CE trends, shows that the interaction of GHI with
the clouds through this 30 year period, is a dynamic phenomenon that's
needs further investigation. Although, to approach it, we need more long
term observations of AOD and clouds characteristics.

@@
